The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
98 tau section

%  HR 6773  is an SPB EB

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.

>>>>

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion. There are an unusually high number of background stars in the same photometric aperture as 98~Tau, and these were not all detected by \texttt{deathstar} and significantly contaminated the resulting lightcurve. As a result it was necessary to manually flag these objects using the `interact' mode of \texttt{lightkurve}, as displayed in Figure~\ref{fig:98tau}. The eclipse is deep enough to be seen by eye in the diffuse light of 98~Tau using this interactive display, and is not associated with any of the background stars.
